---
title: "Untitled"
output: html_document
---

---
  title: "Buoy_Data_QC_Pipeline"
output: html_document
---
  
```{r, library}
library("tidyverse")
library("lubridate")
library("oce")
library('ggplot2')
library('ggpubr')
library('plyr')
library('scales')
library('readr')
library('httr')
library('jsonlite')
```


```{r}
end_date <-parse_date_time(Sys.Date(), c("%y-%m-%d"))#pulls current system date
start_date <-end_date - days(7) #subtracts 7 days to get week range


date_range <-sprintf("%s,%s", start_date, end_date)
graph_date_range<-sprintf("%s_%s", start_date, end_date)

#Pull the last week of data from the Brown API for Buoy-720
Hydrocat_720 = GET(sprintf("https://tech.marecotec.com/ricaim/pumpstation/database/api.php/records/720_Hydrocat?filter=TmStamp,bt,%s",date_range))
Hydrocat_720 = fromJSON(rawToChar(Hydrocat_720$content))
Hydrocat_720 <- Hydrocat_720$records

Suna_720 = GET(sprintf("https://tech.marecotec.com/ricaim/pumpstation/database/api.php/records/720_SUNA?filter=TmStamp,bt,%s",date_range))
Suna_720 = fromJSON(rawToChar(Suna_720$content))
Suna_720 <- Suna_720$records

ECO_720 = GET(sprintf("https://tech.marecotec.com/ricaim/pumpstation/database/api.php/records/720_ECO?filter=TmStamp,bt,%s",date_range))
ECO_720 = fromJSON(rawToChar(ECO_720$content))
ECO_720 <- ECO_720$records

MetData_720 = GET(sprintf("https://tech.marecotec.com/ricaim/pumpstation/database/api.php/records/720_MetData?filter=TmStamp,bt,%s",date_range))
MetData_720 = fromJSON(rawToChar(MetData_720$content))
MetData_720 <- MetData_720$records

Hydrocycle_720 = GET(sprintf("https://tech.marecotec.com/ricaim/pumpstation/database/api.php/records/720_Hydrocycle?filter=TmStamp,bt,%s",date_range))
Hydrocycle_720 = fromJSON(rawToChar(Hydrocycle_720$content))
Hydrocycle_720 <- Hydrocycle_720$records

PAR_720 = GET(sprintf("https://tech.marecotec.com/ricaim/pumpstation/database/api.php/records/720_PAR?filter=TmStamp,bt,%s",date_range))
PAR_720 = fromJSON(rawToChar(PAR_720$content))
PAR_720 <- PAR_720$records

#Parse date/time values using Lubridate 

Hydrocat_720$`TmStamp` <- parse_date_time(Hydrocat_720$TmStamp, c("%y/%m/%d %H:%M:%S"))

ECO_720$`TmStamp` <- parse_date_time(ECO_720$TmStamp, c("%y/%m/%d %H:%M:%S"))
  
Suna_720$`TmStamp` <- parse_date_time(Suna_720$`TmStamp`, c("%y/%m/%d %H:%M:%S"))
  
MetData_720$`TmStamp` <- parse_date_time(MetData_720$`TmStamp`, c("%y/%m/%d %H:%M:%S"))
  
PAR_720$`TmStamp` <- parse_date_time(PAR_720$`TmStamp`, c("%y/%m/%d %H:%M:%S"))

Hydrocycle_720$`TmStamp` <- parse_date_time(Hydrocycle_720$`TmStamp`, c("%y/%m/%d %H:%M:%S"))

month_range <- (range(month(PAR_720$`TmStamp`))) #create month range of collected data to be used for filtering Narragansett Bay historical data by season


#Pull the last week of data from the Brown API for Buoy-620
Hydrocat_620 = GET(sprintf("https://tech.marecotec.com/ricaim/pumpstation/database/api.php/records/620_Hydrocat?filter=TmStamp,bt,%s",date_range))
Hydrocat_620 = fromJSON(rawToChar(Hydrocat_620$content))
Hydrocat_620 <- Hydrocat_620$records

Suna_620 = GET(sprintf("https://tech.marecotec.com/ricaim/pumpstation/database/api.php/records/620_SUNA?filter=TmStamp,bt,%s",date_range))
Suna_620 = fromJSON(rawToChar(Suna_620$content))
Suna_620 <- Suna_620$records

ECO_620 = GET(sprintf("https://tech.marecotec.com/ricaim/pumpstation/database/api.php/records/620_ECO?filter=TmStamp,bt,%s",date_range))
ECO_620 = fromJSON(rawToChar(ECO_620$content))
ECO_620 <- ECO_620$records

MetData_620 = GET(sprintf("https://tech.marecotec.com/ricaim/pumpstation/database/api.php/records/620_MetData?filter=TmStamp,bt,%s",date_range))
MetData_620 = fromJSON(rawToChar(MetData_620$content))
MetData_620 <- MetData_620$records

Hydrocycle_620 = GET(sprintf("https://tech.marecotec.com/ricaim/pumpstation/database/api.php/records/620_Hydrocycle?filter=TmStamp,bt,%s",date_range))
Hydrocycle_620 = fromJSON(rawToChar(Hydrocycle_620$content))
Hydrocycle_620 <- Hydrocycle_620$records

PAR_620 = GET(sprintf("https://tech.marecotec.com/ricaim/pumpstation/database/api.php/records/620_PAR?filter=TmStamp,bt,%s",date_range))
PAR_620 = fromJSON(rawToChar(PAR_620$content))
PAR_620 <- PAR_620$records

#Parse date/time values using Lubridate 

Hydrocat_620$`TmStamp` <- parse_date_time(Hydrocat_620$TmStamp, c("%y/%m/%d %H:%M:%S"))

ECO_620$`TmStamp` <- parse_date_time(ECO_620$TmStamp, c("%y/%m/%d %H:%M:%S"))
  
Suna_620$`TmStamp` <- parse_date_time(Suna_620$`TmStamp`, c("%y/%m/%d %H:%M:%S"))
  
MetData_620$`TmStamp` <- parse_date_time(MetData_620$`TmStamp`, c("%y/%m/%d %H:%M:%S"))
  
PAR_620$`TmStamp` <- parse_date_time(PAR_620$`TmStamp`, c("%y/%m/%d %H:%M:%S"))

Hydrocycle_620$`TmStamp` <- parse_date_time(Hydrocycle_620$`TmStamp`, c("%y/%m/%d %H:%M:%S"))

month_range <- (range(month(PAR_620$`TmStamp`))) #create month range of collected data to be used for filtering Narragansett Bay historical data by season




```


```{r reference_despike_data} 
#Despike data through median smoothing approach and write into a new column. 


Hydrocat_720$Oxygen_despike <- despike(Hydrocat_720$`hydrocatDissOxygen`,reference = c("median"),n = 2,k = 7,replace = c("reference"))

Hydrocat_720$ph_despike <- despike(Hydrocat_720$`hydrocatPH`,reference = c("median"),n = 2,k = 7,replace = c("reference"))

Hydrocat_720$Temperature_despike <- despike(Hydrocat_720$`hydrocatTemperature`,reference = c("median"),n = 2,k = 7,replace = c("reference"))

Hydrocat_720$salinity_despike <- despike(Hydrocat_720$`hydrocatSalinity`,reference = c("median"),n = 2,k = 7,replace = c("reference"))

ECO_720$FDOM_despike<- despike(ECO_720$`ecoFDOM`,reference = c("median"), n=2, k=7, replace = c("reference"))

Suna_720$Nitrate_despike <- despike(Suna_720$`sunaNitrateMicroMol`,reference = c("median"), n=2, k=7, replace = c("reference"))

Hydrocycle_720$Phosphate_despike <- despike(Hydrocycle_720$'CAPO4',reference = c("median"), n=2, k=7, replace = c("reference"))



Hydrocat_620$Oxygen_despike <- despike(Hydrocat_620$`hydrocatDissOxygen`,reference = c("median"),n = 2,k = 7,replace = c("reference"))

Hydrocat_620$ph_despike <- despike(Hydrocat_620$`hydrocatPH`,reference = c("median"),n = 2,k = 7,replace = c("reference"))

Hydrocat_620$Temperature_despike <- despike(Hydrocat_620$`hydrocatTemperature`,reference = c("median"),n = 2,k = 7,replace = c("reference"))

Hydrocat_620$salinity_despike <- despike(Hydrocat_620$`hydrocatSalinity`,reference = c("median"),n = 2,k = 7,replace = c("reference"))

ECO_620$FDOM_despike <- despike(ECO_620$`ecoFDOM`,reference = c("median"), n=2, k=7, replace = c("reference"))

Suna_620$Nitrate_despike <- despike(Suna_620$`sunaNitrateMicroMol`,reference = c("median"), n=2, k=7, replace = c("reference"))

Hydrocycle_620$Phosphate_despike <- despike(Hydrocycle_620$'CAPO4',reference = c("median"), n=2, k=7, replace = c("reference"))

```

```{r Global Data Range}
#Perform range check for applicable variables against global historical measurement range, flag with QC Flags (1=low, 2=high, 0=good) 
global_range_data <- read.csv('D:/work/data_qc_global_range_values.csv', header=TRUE, sep=",", na.strings=c(""))

global_range_data_wide <-global_range_data %>% 
  pivot_wider(names_from = ParameterID_R, values_from =c(GlobalRangeMax, GlobalRangeMin))

global_psu_max <- max(range(global_range_data_wide$GlobalRangeMax_practical_salinity))
global_psu_min <- min(range(global_range_data_wide$GlobalRangeMin_practical_salinity))
global_temp_max <- max(range(global_range_data_wide$GlobalRangeMax_seawater_temperature))
global_temp_min <- min(range(global_range_data_wide$GlobalRangeMin_seawater_temperature))
global_chla_max <- min(range(global_range_data_wide$GlobalRangeMax_fluorometric_chlorophyll_a))
global_chla_min <- min(range(global_range_data_wide$GlobalRangeMin_fluorometric_chlorophyll_a))
global_ph_max <- min(range(global_range_data_wide$GlobalRangeMax_ph_seawater))
global_ph_min <- min(range(global_range_data_wide$GlobalRangeMin_ph_seawater))
global_oxy_max <- max(range(global_range_data_wide$GlobalRangeMax_dissolved_oxygen))
global_oxy_min <- min(range(global_range_data_wide$GlobalRangeMin_dissolved_oxygen))
global_fluoro_max <- max(range(global_range_data_wide$GlobalRangeMax_fluorometric_cdom))
global_fluoro_min <- min(range(global_range_data_wide$GlobalRangeMin_fluorometric_cdom))
global_nitrate_max <- max(range(global_range_data_wide$GlobalRangeMax_nitrate_concentration))
global_nitrate_min <- min(range(global_range_data_wide$GlobalRangeMin_nitrate_concentration))
global_phosphate_max <- max(range(global_range_data_wide$GlobalRangeMax_nitrate_concentration))
global_phosphate_min <- min(range(global_range_data_wide$GlobalRangeMin_))

#Range check against global values
Hydrocat_720 <-mutate(Hydrocat_720,
                      Salinity_Global_Range_QC =ifelse(Hydrocat_720$`salinity_despike` > global_psu_max,
                                                             "2",ifelse( Hydrocat_720$`salinity_despike` < global_psu_min,"1","0"))) 
Hydrocat_720 <-mutate(Hydrocat_720,
                     Temp_Global_Range_QC =ifelse(Hydrocat_720$`Temperature_despike` > global_temp_max,
                                                             "2",ifelse( Hydrocat_720$`Temperature_despike` < global_temp_min,"1","0")))
Hydrocat_720 <-mutate(Hydrocat_720,
                     ph_Global_Range_QC =ifelse(Hydrocat_720$`ph_despike` > global_ph_max,
                                                             "2",ifelse( Hydrocat_720$`ph_despike` < global_ph_min,"1","0")))
Hydrocat_720 <-mutate(Hydrocat_720,
                     oxy_Global_Range_QC =ifelse(Hydrocat_720$`Oxygen_despike` > global_oxy_max,
                                                             "2",ifelse( Hydrocat_720$`Oxygen_despike` < global_oxy_min,"1","0")))

ECO_720 <- mutate(ECO_720,
                   FDOM_Global_Range_QC = ifelse(ECO_720$`FDOM_despike` > global_fluoro_max,
                                                 "2", ifelse(ECO_720$`FDOM_despike` < global_fluoro_min,"1","0")))

Suna_720 <- mutate(Suna_720,
                    Nitrate_Global_Range_QC = ifelse(Suna_720$`Nitrate_despike` > global_nitrate_max,
                                                 "2", ifelse(Suna_720$`Nitrate_despike` < global_nitrate_min,"1","0")))
#Hydrocyle_720-week <- mutate(Hydrocycle_720,
#                    Nitrate_Global_Range_QC = ifelse(Suna_720$`Nitrate_despike` > global_nitrate_max,
#                                                 "2", ifelse(Suna_720$`Nitrate_despike` < global_nitrate_min,"1","0")))

Hydrocat_620 <-mutate(Hydrocat_620,
                      Salinity_Global_Range_QC =ifelse(Hydrocat_620$`salinity_despike` > global_psu_max,
                                                             "2",ifelse( Hydrocat_620$`salinity_despike` < global_psu_min,"1","0"))) 
Hydrocat_620 <-mutate(Hydrocat_620,
                     Temp_Global_Range_QC =ifelse(Hydrocat_620$`Temperature_despike` > global_temp_max,
                                                             "2",ifelse( Hydrocat_620$`Temperature_despike` < global_temp_min,"1","0")))
Hydrocat_620 <-mutate(Hydrocat_620,
                     ph_Global_Range_QC =ifelse(Hydrocat_620$`ph_despike` > global_ph_max,
                                                             "2",ifelse( Hydrocat_620$`ph_despike` < global_ph_min,"1","0")))
Hydrocat_620 <-mutate(Hydrocat_620,
                     oxy_Global_Range_QC =ifelse(Hydrocat_620$`Oxygen_despike` > global_oxy_max,
                                                             "2",ifelse( Hydrocat_620$`Oxygen_despike` < global_oxy_min,"1","0")))

ECO_620 <- mutate(ECO_620,
                   FDOM_Global_Range_QC = ifelse(ECO_620$`FDOM_despike` > global_fluoro_max,
                                                 "2", ifelse(ECO_620$`FDOM_despike` < global_fluoro_min,"1","0")))

Suna_620 <- mutate(Suna_620,
                    Nitrate_Global_Range_QC = ifelse(Suna_620$`Nitrate_despike` > global_nitrate_max,
                                                 "2", ifelse(Suna_620$`Nitrate_despike` < global_nitrate_min,"1","0")))




```


```{r Narragansett Bay Seasonal Range}
nb_hist_phys_data <- read.csv('D:/work/NB_PhysicalData_8.10.20201.csv', header=TRUE, sep=",", na.strings=c("","nd")) #Read in historical physical data from GSO LTS measurements


nb_hist_phys_data$Date <- parse_date_time(nb_hist_phys_data$Date, c("%d-%m-%y")) #Parse Date column into date objects

nb_hist_phys_seasonal_filter <- nb_hist_phys_data %>% filter(month(nb_hist_phys_data$Date) >= min(month_range) & month(nb_hist_phys_data$Date) <= max(month_range))   #Filter historical data to seasonal time frame of buoy data

seasonal_nb_psu_range <- range(nb_hist_phys_seasonal_filter$Surface_Salinity,na.rm = TRUE)

seasonal_nb_surface_temp_range <- range(nb_hist_phys_seasonal_filter$Surface_Temp,na.rm = TRUE)




nb_hist_nutr_data <- read.csv('D:/work/nutrientdata_01.18.2021.csv', header=TRUE, sep=",", na.strings=c("","nd")) #Read in historical nutrient data from GSO LTS measurements

nb_hist_nutr_data$Date <- parse_date_time(nb_hist_nutr_data$Date, c("%m/%d/%y")) #Parse Date column into date objects

nb_hist_nutr_seasonal_filter <- nb_hist_nutr_data %>% filter(month(nb_hist_nutr_data$Date) >= min(month_range) & month(nb_hist_nutr_data$Date) <= max(month_range))   #Filter historical data to seasonal time frame of buoy data

seasonal_nb_nitrate_range <- range(nb_hist_nutr_seasonal_filter$NO3_uM,na.rm = TRUE)

seasonal_nb_DIP_range <- range(nb_hist_nutr_seasonal_filter$DIP_uM,na.rm = TRUE)


#Range check against seasonal Narragansett Bay global values
Hydrocat_720 <-mutate(Hydrocat_720,
                      Salinity_Seasonal_NB_Range_QC =ifelse(Hydrocat_720$`salinity_despike` >  max(seasonal_nb_psu_range),
                                                             "2",ifelse( Hydrocat_720$`salinity_despike` < min(seasonal_nb_psu_range),"1","0"))) 
Hydrocat_720 <-mutate(Hydrocat_720,
                     Temp_Seasonal_NB_Range_QC =ifelse(Hydrocat_720$`Temperature_despike` > max(seasonal_nb_surface_temp_range),
                                                             "2",ifelse( Hydrocat_720$`Temperature_despike` < min(seasonal_nb_surface_temp_range),"1","0")))

Suna_720 <- mutate(Suna_720,
                    Nitrate_Global_Range_QC = ifelse(Suna_720$`Nitrate_despike` > max(seasonal_nb_nitrate_range),
                                                 "2", ifelse(Suna_720$`Nitrate_despike` < min(seasonal_nb_nitrate_range),"1","0")))
Hydrocycle_720 <- mutate(Hydrocycle_720,
                    Phosphate_Seasonal_NB_Range_QC = ifelse(Hydrocycle_720$Phosphate_despike > max(seasonal_nb_DIP_range),
                                                 "2", ifelse(Hydrocycle_720$Phosphate_despike < min(seasonal_nb_DIP_range),"1","0")))




Hydrocat_620 <-mutate(Hydrocat_620,
                      Salinity_Seasonal_NB_Range_QC =ifelse(Hydrocat_620$`salinity_despike` >  max(seasonal_nb_psu_range),
                                                             "2",ifelse( Hydrocat_620$`salinity_despike` < min(seasonal_nb_psu_range),"1","0"))) 
Hydrocat_620 <-mutate(Hydrocat_620,
                     Temp_Seasonal_NB_Range_QC =ifelse(Hydrocat_620$`Temperature_despike` > max(seasonal_nb_surface_temp_range),
                                                             "2",ifelse( Hydrocat_620$`Temperature_despike` < min(seasonal_nb_surface_temp_range),"1","0")))

Suna_620 <- mutate(Suna_620,
                    Nitrate_Global_Range_QC = ifelse(Suna_620$`Nitrate_despike` > max(seasonal_nb_nitrate_range),
                                                 "2", ifelse(Suna_620$`Nitrate_despike` < min(seasonal_nb_nitrate_range),"1","0")))
Hydrocycle_620 <- mutate(Hydrocycle_620,
                    Phosphate_Seasonal_NB_Range_QC = ifelse(Hydrocycle_620$Phosphate_despike > max(seasonal_nb_DIP_range),
                                                 "2", ifelse(Hydrocycle_620$Phosphate_despike < min(seasonal_nb_DIP_range),"1","0")))




```
Hydro_Salinity_720 <- ggplot(Hydrocat_720,aes(x=`TmStamp`, y=salinity_despike, color=Salinity_Global_Range_QC)) + (scale_x_datetime(breaks = date_breaks("1 day"),
        labels = date_format("%m/%d")))  +  geom_line() + scale_color_manual(breaks = c("0", "1", "2"),values=c("#009900", "#00CCCC", "#CC0000")) + ylab('Salinity (psu)') +         xlab('Date')+  theme_bw() +
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        axis.text.x=element_text(angle=0)) +
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=14,face="bold"))


Hydro_Temp_720 <- ggplot(Hydrocat_720,aes(x=`TmStamp`, y=Temperature_despike, color=Temp_Global_Range_QC )) + (scale_x_datetime(breaks = date_breaks("1 day"),
        labels = date_format("%m/%d")))  +  geom_line() + scale_color_manual(breaks = c("0", "1", "2"),values=c("#009900", "#00CCCC", "#CC0000")) + ylab('Temperature (Celcius)') +   xlab('Date')+  theme_bw() +
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        axis.text.x=element_text(angle=0)) +
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=14,face="bold"))


Hydro_pH_720 <- ggplot(Hydrocat_720,aes(x=`TmStamp`, y=ph_despike, color=ph_Global_Range_QC )) + (scale_x_datetime(breaks = date_breaks("1 day"),
        labels = date_format("%m/%d")))  +  geom_line() + scale_color_manual(breaks = c("0", "1", "2"),values=c("#009900", "#00CCCC", "#CC0000")) + ylab('pH') + xlab('Date')+       theme_bw() +
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        axis.text.x=element_text(angle=0)) +
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=14,face="bold"))


Hydro_oxy_720 <- ggplot(Hydrocat_720,aes(x=`TmStamp`, y=Oxygen_despike, color=oxy_Global_Range_QC )) + (scale_x_datetime(breaks = date_breaks("1 day"),
        labels = date_format("%m/%d")))  +  geom_line() + scale_color_manual(breaks = c("0", "1", "2"),values=c("#009900", "#00CCCC", "#CC0000")) + ylab('Dissolved Oxygen (mg/L)')   + xlab('Date')+  theme_bw() +
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        axis.text.x=element_text(angle=0)) +
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=14,face="bold"))
```{r despike_QC_timeseries_plots}
#Plot desired time series line plots in grid format.Lines are plotted for visual inspection, and colored by QC range flags.
file_path_720 <- sprintf("D:/work/720_Weekly_Plots_%s.pdf",graph_date_range)
pdf(file=file_path_720,width=16,height=12,useDingbats=FALSE)#open pdf graphical object to plot as pdf


Wind_720_Plot <- ggplot(MetData_720,aes(x=`TmStamp`, y=avgWindSpeed)) + (scale_x_datetime(breaks = date_breaks("1 day"),
  labels = date_format("%m/%d")))  +  geom_line() + ylab('Average Wind Speed (m/s)') + xlab('Date')+  theme_bw() +
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        axis.text.x=element_text(angle=0)) +
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=14,face="bold"))

Temperature_720_Plot <- ggplot(MetData_720,aes(x=`TmStamp`, y=maximetTemperature)) + (scale_x_datetime(breaks = date_breaks("1 day"),
  labels = date_format("%m/%d")))  +  geom_line() + ylab('Temperature (Celcius)') + xlab('Date')+  theme_bw() +
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        axis.text.x=element_text(angle=0)) +
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=14,face="bold"))

Humidity_720_Plot <- ggplot(MetData_720,aes(x=`TmStamp`, y=maximetHumidity)) + (scale_x_datetime(breaks = date_breaks("1 day"),
  labels = date_format("%m/%d")))  +  geom_line() + ylab('Humidity (%)') + xlab('Date')+  theme_bw() +
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        axis.text.x=element_text(angle=0)) +
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=14,face="bold"))

Pressure_720_Plot <- ggplot(MetData_720,aes(x=`TmStamp`, y=maximetPressure)) + (scale_x_datetime(breaks = date_breaks("1 day"),
  labels = date_format("%m/%d")))  +  geom_line() + ylab('Pressure (db)') + xlab('Date')+  theme_bw() +
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        axis.text.x=element_text(angle=0)) +
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=14,face="bold"))

Precipitation_720_Plot <- ggplot(MetData_720,aes(x=`TmStamp`, y=maximetPrecipitation)) + (scale_x_datetime(breaks = date_breaks("1 day"),
  labels = date_format("%m/%d")))  +  geom_line() + ylab('Precipitation (mm/Hr)') + xlab('Date')+  theme_bw() +
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        axis.text.x=element_text(angle=0)) +
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=14,face="bold"))


Suna_720_plot <- ggplot(Suna_720,aes(x=`TmStamp`, y=Nitrate_despike, color=Nitrate_Global_Range_QC)) + (scale_x_datetime(breaks = date_breaks("1 day"),
  labels = date_format("%m/%d")))  +  geom_line() + scale_color_manual(breaks = c("0", "1", "2"),values=c("#009900", "#00CCCC", "#CC0000")) + ylab('Nitrate (umol)') + xlab('Date')+  theme_bw() +
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        axis.text.x=element_text(angle=0)) +
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=14,face="bold"))

ECO_720_plot <- ggplot(ECO_720,aes(x=`TmStamp`,y=ecoReadingRaw, color=FDOM_Global_Range_QC)) + (scale_x_datetime(breaks = date_breaks("1 day"),
  labels = date_format("%m/%d")))  +  geom_line() + scale_color_manual(breaks = c("0", "1", "2"),values=c("#009900", "#00CCCC", "#CC0000")) + ylab('FDOM (ppb)') + xlab('Date') +  theme_bw() +
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        axis.text.x=element_text(angle=0)) +
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=14,face="bold"))

Hydrocycle_720_plot <- ggplot(Hydrocycle_720,aes(x=`TmStamp`,y=Phosphate_despike, color=Phosphate_Seasonal_NB_Range_QC)) + (scale_x_datetime(breaks = date_breaks("1 day"),
  labels = date_format("%m/%d")))  +  geom_line() + scale_color_manual(breaks = c("0", "1", "2"),values=c("#009900", "#00CCCC", "#CC0000")) + ylab('Phosphate (uM)') + xlab('Date') +  theme_bw() +
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        axis.text.x=element_text(angle=0)) +
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=14,face="bold"))

qc_arrange <- ggarrange(ECO_720_plot,Suna_720_plot,Precipitation_720_Plot,Pressure_720_Plot,Humidity_720_Plot,Temperature_720_Plot, Wind_720_Plot,Hydrocycle_720_plot, nrow = 5)
#Hydro_oxy_720,Hydro_pH_720,Hydro_Temp_720,Hydro_Salinity_720,

qc_arrange
dev.off()#close pdf

#Plot desired time series line plots in grid format.Lines are plotted for visual inspection, and colored by QC range flags.
file_path_620 <- sprintf("D:/work/620_Weekly_Plots_%s.pdf",graph_date_range)
pdf(file=file_path_620,width=16,height=12,useDingbats=FALSE)#open pdf graphical object to plot as pdf


Hydro_Salinity_620 <- ggplot(Hydrocat_620,aes(x=`TmStamp`, y=salinity_despike, color=Salinity_Global_Range_QC)) + (scale_x_datetime(breaks = date_breaks("1 day"),
        labels = date_format("%m/%d")))  +  geom_line() + scale_color_manual(breaks = c("0", "1", "2"),values=c("#009900", "#00CCCC", "#CC0000")) + ylab('Salinity (psu)') +         xlab('Date')+  theme_bw() +
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        axis.text.x=element_text(angle=0)) +
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=14,face="bold"))


Hydro_Temp_620 <- ggplot(Hydrocat_620,aes(x=`TmStamp`, y=Temperature_despike, color=Temp_Global_Range_QC )) + (scale_x_datetime(breaks = date_breaks("1 day"),
        labels = date_format("%m/%d")))  +  geom_line() + scale_color_manual(breaks = c("0", "1", "2"),values=c("#009900", "#00CCCC", "#CC0000")) + ylab('Temperature (Celcius)') +   xlab('Date')+  theme_bw() +
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        axis.text.x=element_text(angle=0)) +
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=14,face="bold"))


Hydro_pH_620 <- ggplot(Hydrocat_620,aes(x=`TmStamp`, y=ph_despike, color=ph_Global_Range_QC )) + (scale_x_datetime(breaks = date_breaks("1 day"),
        labels = date_format("%m/%d")))  +  geom_line() + scale_color_manual(breaks = c("0", "1", "2"),values=c("#009900", "#00CCCC", "#CC0000")) + ylab('pH') + xlab('Date')+       theme_bw() +
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        axis.text.x=element_text(angle=0)) +
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=14,face="bold"))


Hydro_oxy_620 <- ggplot(Hydrocat_620,aes(x=`TmStamp`, y=Oxygen_despike, color=oxy_Global_Range_QC )) + (scale_x_datetime(breaks = date_breaks("1 day"),
        labels = date_format("%m/%d")))  +  geom_line() + scale_color_manual(breaks = c("0", "1", "2"),values=c("#009900", "#00CCCC", "#CC0000")) + ylab('Dissolved Oxygen (mg/L)')   + xlab('Date')+  theme_bw() +
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        axis.text.x=element_text(angle=0)) +
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=14,face="bold"))


Wind_620_Plot <- ggplot(MetData_620,aes(x=`TmStamp`, y=avgWindSpeed)) + (scale_x_datetime(breaks = date_breaks("1 day"),
  labels = date_format("%m/%d")))  +  geom_line() + ylab('Average Wind Speed (m/s)') + xlab('Date')+  theme_bw() +
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        axis.text.x=element_text(angle=0)) +
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=14,face="bold"))

Temperature_620_Plot <- ggplot(MetData_620,aes(x=`TmStamp`, y=maximetTemperature)) + (scale_x_datetime(breaks = date_breaks("1 day"),
  labels = date_format("%m/%d")))  +  geom_line() + ylab('Temperature (Celcius)') + xlab('Date')+  theme_bw() +
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        axis.text.x=element_text(angle=0)) +
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=14,face="bold"))

Humidity_620_Plot <- ggplot(MetData_620,aes(x=`TmStamp`, y=maximetHumidity)) + (scale_x_datetime(breaks = date_breaks("1 day"),
  labels = date_format("%m/%d")))  +  geom_line() + ylab('Humidity (%)') + xlab('Date')+  theme_bw() +
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        axis.text.x=element_text(angle=0)) +
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=14,face="bold"))

Pressure_620_Plot <- ggplot(MetData_620,aes(x=`TmStamp`, y=maximetPressure)) + (scale_x_datetime(breaks = date_breaks("1 day"),
  labels = date_format("%m/%d")))  +  geom_line() + ylab('Pressure (db)') + xlab('Date')+  theme_bw() +
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        axis.text.x=element_text(angle=0)) +
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=14,face="bold"))

Precipitation_620_Plot <- ggplot(MetData_620,aes(x=`TmStamp`, y=maximetPrecipitation)) + (scale_x_datetime(breaks = date_breaks("1 day"),
  labels = date_format("%m/%d")))  +  geom_line() + ylab('Precipitation (mm/Hr)') + xlab('Date')+  theme_bw() +
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        axis.text.x=element_text(angle=0)) +
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=14,face="bold"))


Suna_620_plot <- ggplot(Suna_620,aes(x=`TmStamp`, y=Nitrate_despike, color=Nitrate_Global_Range_QC)) + (scale_x_datetime(breaks = date_breaks("1 day"),
  labels = date_format("%m/%d")))  +  geom_line() + scale_color_manual(breaks = c("0", "1", "2"),values=c("#009900", "#00CCCC", "#CC0000")) + ylab('Nitrate (umol)') + xlab('Date')+  theme_bw() +
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        axis.text.x=element_text(angle=0)) +
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=14,face="bold"))

ECO_620_plot <- ggplot(ECO_620,aes(x=`TmStamp`,y=ecoReadingRaw, color=FDOM_Global_Range_QC)) + (scale_x_datetime(breaks = date_breaks("1 day"),
  labels = date_format("%m/%d")))  +  geom_line() + scale_color_manual(breaks = c("0", "1", "2"),values=c("#009900", "#00CCCC", "#CC0000")) + ylab('FDOM (ppb)') + xlab('Date') +  theme_bw() +
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        axis.text.x=element_text(angle=0)) +
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=14,face="bold"))

ECO_620_plot <- ggplot(ECO_620,aes(x=`TmStamp`,y=FDOM_despike, color=FDOM_Global_Range_QC)) + (scale_x_datetime(breaks = date_breaks("1 day"),
  labels = date_format("%m/%d")))  +  geom_line() + scale_color_manual(breaks = c("0", "1", "2"),values=c("#009900", "#00CCCC", "#CC0000")) + ylab('FDOM (ppb)') + xlab('Date') +  theme_bw() +
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        axis.text.x=element_text(angle=0)) +
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=14,face="bold"))

Hydrocycle_620_plot <- ggplot(Hydrocycle_620,aes(x=`TmStamp`,y=Phosphate_despike, color=Phosphate_Seasonal_NB_Range_QC)) + (scale_x_datetime(breaks = date_breaks("1 day"),
  labels = date_format("%m/%d")))  +  geom_line() + scale_color_manual(breaks = c("0", "1", "2"),values=c("#009900", "#00CCCC", "#CC0000")) + ylab('Phosphate (uM)') + xlab('Date') +  theme_bw() +
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        axis.text.x=element_text(angle=0)) +
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=14,face="bold"))

qc_arrange <- ggarrange(ECO_620_plot,Suna_620_plot,Precipitation_620_Plot,Pressure_620_Plot,Humidity_620_Plot,Temperature_620_Plot, Wind_620_Plot,Hydro_oxy_620,Hydro_pH_620,Hydro_Temp_620,Hydro_Salinity_620,Hydrocycle_620_plot, nrow = 5)

qc_arrange
dev.off()#close pdf

```

```{r}

pdf(file="D:/work/620_720_ECO_Plots_9_14_2021.pdf",width=16,height=12,useDingbats=FALSE)#open pdf graphical object to plot as pdf
ECO_620_raw_plot <- ggplot(ECO_620,aes(x=`TmStamp`,y=ecoReadingRaw)) + (scale_x_datetime(breaks = date_breaks("1 day"),
  labels = date_format("%m/%d")))  +  geom_line() + scale_color_manual(breaks = c("0", "1", "2"),values=c("#009900", "#00CCCC", "#CC0000")) + ylab('620 ECO Raw Counts ') + xlab('Date') +  theme_bw() +
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        axis.text.x=element_text(angle=45,vjust=0.5)) +
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=14,face="bold"))

ECO_620_fdom_plot <- ggplot(ECO_620,aes(x=`TmStamp`,y=FDOM_despike)) + (scale_x_datetime(breaks = date_breaks("1 day"),
  labels = date_format("%m/%d")))  +  geom_line() + scale_color_manual(breaks = c("0", "1", "2"),values=c("#009900", "#00CCCC", "#CC0000")) + ylab('620 ECO FDOM (ppb)') + xlab('Date') +  theme_bw() +
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        axis.text.x=element_text(angle=45,vjust=0.5)) +
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=14,face="bold"))

ECO_620_channel_plot <- ggplot(ECO_620,aes(x=`TmStamp`,y=ecoChannel)) + (scale_x_datetime(breaks = date_breaks("1 day"),
  labels = date_format("%m/%d")))  +  geom_line() + scale_color_manual(breaks = c("0", "1", "2"),values=c("#009900", "#00CCCC", "#CC0000")) + ylab('620 ECO Channel ') + xlab('Date') +  theme_bw() +
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        axis.text.x=element_text(angle=45,vjust=0.5)) +
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=14,face="bold"))

ECO_620_wavelength_plot <- ggplot(ECO_620,aes(x=`TmStamp`,y=ecoWavelength)) + (scale_x_datetime(breaks = date_breaks("1 day"),
  labels = date_format("%m/%d")))  +  geom_line() + scale_color_manual(breaks = c("0", "1", "2"),values=c("#009900", "#00CCCC", "#CC0000")) + ylab('620 ECO Wavelength') + xlab('Date') +  theme_bw() +
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        axis.text.x=element_text(angle=45,vjust=0.5)) +
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=14,face="bold"))


ECO_720_raw_plot <- ggplot(ECO_720,aes(x=`TmStamp`,y=ecoReadingRaw)) + (scale_x_datetime(breaks = date_breaks("1 day"),
  labels = date_format("%m/%d")))  +  geom_line() + scale_color_manual(breaks = c("0", "1", "2"),values=c("#009900", "#00CCCC", "#CC0000")) + ylab('720 ECO Raw Counts ') + xlab('Date') +  theme_bw() +
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        axis.text.x=element_text(angle=45,vjust=0.5)) +
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=14,face="bold"))

ECO_720_fdom_plot <- ggplot(ECO_720,aes(x=`TmStamp`,y=FDOM_despike)) + (scale_x_datetime(breaks = date_breaks("1 day"),
  labels = date_format("%m/%d")))  +  geom_line() + scale_color_manual(breaks = c("0", "1", "2"),values=c("#009900", "#00CCCC", "#CC0000")) + ylab('720 ECO FDOM (ppb)') + xlab('Date') +  theme_bw() +
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        axis.text.x=element_text(angle=45,vjust=0.5)) +
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=14,face="bold"))

ECO_720_channel_plot <- ggplot(ECO_720,aes(x=`TmStamp`,y=ecoChannel)) + (scale_x_datetime(breaks = date_breaks("1 day"),
  labels = date_format("%m/%d")))  +  geom_line() + scale_color_manual(breaks = c("0", "1", "2"),values=c("#009900", "#00CCCC", "#CC0000")) + ylab('720 ECO Channel ') + xlab('Date') +  theme_bw() +
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        axis.text.x=element_text(angle=45,vjust=0.5)) +
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=14,face="bold"))

ECO_720_wavelength_plot <- ggplot(ECO_720,aes(x=`TmStamp`,y=ecoWavelength)) + (scale_x_datetime(breaks = date_breaks("1 day"),
  labels = date_format("%m/%d")))  +  geom_line() + scale_color_manual(breaks = c("0", "1", "2"),values=c("#009900", "#00CCCC", "#CC0000")) + ylab('720 ECO Wavelength') + xlab('Date') +  theme_bw() +
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        axis.text.x=element_text(angle=45,vjust=0.5)) +
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=14,face="bold"))


qc_arrange <- ggarrange(ECO_720_raw_plot,ECO_720_fdom_plot,ECO_720_channel_plot, ECO_720_wavelength_plot,ECO_620_raw_plot,ECO_620_fdom_plot,ECO_620_channel_plot, ECO_620_wavelength_plot, nrow = 4)
qc_arrange
dev.off()#close pdf
```

